% -----------------------------------------------------------------------------
% Education
% -----------------------------------------------------------------------------

\begin{ResumeSection}{EDUCATION}

    \begin{DatedField}
        {Kyoto Univeristy, Japan}
        {Mar 2023 - Aug 2023}
        {Kyoto Univeristy International Exchange Program}
        {Sakyo-ku, Kyoto}
        \item Semester exchange in fulfilment of undergraduate Bachelors at the University of Sydney. Recipient of the Australian New Colombo Plan Mobility Program.
        \item \textit{Areas of study}: Japanese culture, history, and politics, statistics, material science, physics, chemical engineering, psychology, and computer simulation.
        \item \textit{Activities and societies}: KUISC (International student committee), Cat-ch (Stray cat rescue), KIU (Soccer club), Downhill (Hiking club), KU Raku Raku (Sightseeing club), ATA (Tennis club), SFT (Study group).
    \end{DatedField}

    \newpage

    \begin{DatedField}
        {Univeristy of Sydney, Australia}
        {Feb 2019 - Nov 2023}
        {Bachelor of Advanced Computing (Honours) / Bachelor of Science (Dalyell Scholarhip)}
        {Camperdown, NSW}
        \item Undergraduate Bachelors degree with Honours from the Faculty of Engineering. Achieved high distinction in Honours thesis. Mentored students across faculties and participated in hackathons.
        \item \textit{Areas of study}: Machine learning, statistics, data analysis, systems programming, algorithmic analysis, optimisation, software development, project management, artificial intelligence, and frontend development.
        \item \textit{Activities and societies}: SUEUA (Engineering), SYNCS (Computer science), SUCES (Chemical engineering), SciSoc (Science), PhySoc (Physics), SUMS (Mathematics), SUDATA (Data science), USYD Dog Society.
    \end{DatedField}

    \begin{DatedField}
        {St Joseph's College, Australia}
        {Feb 2013 - Nov 2018}
        {High School Certificate}
        {Hunters Hill, NSW}
        \item Competed in academic, debating, soccer, and tennis competitions. Participated in inter-school programs and supported students through peer tutoring sessions. Volunteered in disability charity programs.
    \end{DatedField}
    
\end{ResumeSection}