% -----------------------------------------------------------------------------
% Work experience
% -----------------------------------------------------------------------------

\begin{ResumeSection}{EXPERIENCE}

    \begin{DatedField}
        {Junior Data Scientist}
        {Dec 2021 - Present}
        {Pending AI (Cheminformatics)}
        {South Eveleigh, NSW}
        \item Implemented retrosynthesis for reaction data reducing extractions from 10+ minutes to sub-second in Neo4j.
        \item Developed baseline GGMs and simple LLMs for comparative data analysis of production model performance.
        \item Construct pipelines for system-specific cheminformatics library compilation for different programming languages.
        \item Managed Neo4j database security mechanisms, internal procedures, cron jobs, ETL processes, and availability.
        \item Produced visualisations of results and certain metrics, leveraged realtime metrics for availability monitoring.
        \item Product-based PM in a scrum environment, team collaboration such as service communication protocols.
    \end{DatedField}

    \newpage
    
    \begin{DatedField}
        {Software Engineer Intern}
        {Jun 2021 - Dec 2021}
        {Deferit (Financial Technology)}
        {Sydney, NSW}
        \item Automated backend system operations, customer bill payments, data visualisation and web interactions (Agile).
        \item Reviewed and improved the application codebase to assess optimal logic flow and structure for bottlenecks.
        \item Collaborated with separate teams in completing Jira tickets and Confluence documentation for new features.
        \item Constructed NLP frameworks (NER) for accurate bill information extraction and integration into the codebase.
        \item Used JavaScript and VBA for producing internal metrics and visualisations for non-technical teams.
    \end{DatedField}

\end{ResumeSection} 